Individual ABC Fits

### 2024-02-09 Model/abc_reject.qmd
first re-render in awhile, and 2 more reports

#file_name <- "n_iter_300_ntry_3000_0800"
file_name <- "n_iter_100_ntry_200_4509"

@@

## Learning Curves
```{r fig.width=11, fig.height=16}

@@

post_tabs <- map(post_tabs, ~cbind(.x,run_info) |> mutate(fn=file_name))
# path1 = "../../../data/abc_tabs"
saveRDS(post_tabs, paste0(path1, "/", tools::file_path_sans_ext(basename(file_name)),"_post_tab", ".rds"))
saveRDS(post_tabs, paste0(tools::file_path_sans_ext(basename(file_name)),"_post_tab", ".rds"))
```

>>>>

#file_name <- "n_iter_300_ntry_3000_0800"
#file_name <- "n_iter_100_ntry_200_4509"
file_name <- "n_iter_100_ntry_400_3247"

@@

## Learning Curves
```{r fig.width=11, fig.height=16}
#| fig-cap: "Learning Curves"
#| fig-width: 11
#| fig-height: 13

@@

# post_tabs <- map(post_tabs, ~cbind(.x,run_info) |> mutate(fn=file_name))
# # path1 = "../../../data/abc_tabs"
# saveRDS(post_tabs, paste0(path1, "/", tools::file_path_sans_ext(basename(file_name)),"_post_tab", ".rds"))
# saveRDS(post_tabs, paste0(tools::file_path_sans_ext(basename(file_name)),"_post_tab", ".rds"))
```
